Price of Anarchy for Mean Field Games

### 2018-07-27 PoA.tex
minor edits Prop 7 Case 3

	% case 3: b1 to infinity
	\textbf{Case 3:} consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$,
	\begin{equation}
		\lim_{b_1 \to \infty} \frac{u_t^{b_1}}{b_1} =  	\lim_{b_1 \to \infty} \frac{w_t^{b_1}}{b_1} = \frac{2}{B}.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$. From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing, and
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq B \left(\frac{2}{B} +\frac{1}{B} \right) = 3.$$

	Moreover, for any fixed $\epsilon$, there exists $b^{*,I_1}_1(\epsilon) \geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1}(\epsilon) $, and for all $t \in [0, 3/4 T]$,
	$$ \vert h_u(b_1, t) - h_u(b_1,t) \vert  \leq \epsilon, \quad h_w(b_1,0) \geq B \left( \frac{2}{B} - \frac{1}{3B} \right) = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, \frac{3}{4} T) \geq \frac{5}{3}.$$
	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3/4 T]$ and $[3/4 T, T]$. For all $b_2 \geq b_2^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have
	\begin{equation*}
		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)}
	\end{equation*}
	where
	\begin{IEEEeqnarray*}{rCl}
	I_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
	& \leq & \kappa_1 \epsilon^2 
	\end{IEEEeqnarray*} 	
	in which $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
	\begin{IEEEeqnarray*}{rCl}
		 I_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
		 &=& \kappa_2 b_1 e^{- \frac{1}{2} b_1 T}
	\end{IEEEeqnarray*}
	in which $\kappa_2 = 9 T e^{2 \bar{b}_1 T}$.	
	We can continue to choose $b_2$ being even larger, say for example $b_2 \geq b_2^{*}$ with $b_2^{*}(\epsilon) \geq b_2^{*,I_1}(\epsilon)$, so that $ I_2 \leq \epsilon$. Hence, for any given $\epsilon >0$ we obtain that for all $b_1 \geq b_1^{*}(\epsilon)$,
	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon),$$
	thus by letting $\epsilon \to 0$ we conclude that 
	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$

>>>>

	% case 3: b1 to infinity
	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$:
	\begin{equation}
		\lim_{b_1 \to \infty} \frac{u_t^{b_1}}{b_1} =  	\lim_{b_1 \to \infty} \frac{w_t^{b_1}}{b_1} = \frac{2}{B}.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$. From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, we have:
	$$\max \left\{ \left|\frac{u_0^{b_1}}{b_1}-\frac{2}{B} \right|,\left|\frac{w_0^{b_1}}{b_1}-\frac{2}{B} \right| \right\} \leq \frac{1}{B},$$
	and the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing. Thus,
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq B \left(\frac{2}{B} +\frac{1}{B} \right) = 3.$$

	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3/4 T]$,
	$$ \vert h_u(b_1, t) - h_u(b_1,t) \vert  \leq \epsilon, \quad h_w(b_1,0) \geq B \left( \frac{2}{B} - \frac{1}{3B} \right) = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, \frac{3}{4} T) \geq \frac{5}{3}.$$
	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3/4 T]$ and $[3/4 T, T]$. For all $b_1 \geq b_1^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have:
	\begin{equation*}
		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)},
	\end{equation*}
	where
	\begin{IEEEeqnarray*}{rCl}
	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
	&= & \epsilon^2 e^{\frac{3\bar{b}_1 T}{2} } \cdot \frac{3}{4}(1-e^{-b_1T})  \nonumber \\	
	& \leq & \kappa_1 \epsilon^2 ,
	\end{IEEEeqnarray*} 	
	in which $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
	\begin{IEEEeqnarray*}{rCl}
		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
		 &=&  9 T e^{2 \bar{b}_1 T} b_1 e^{- \frac{1}{2} b_1 T} \xrightarrow[b_1 \to \infty]{}0.
	\end{IEEEeqnarray*}
	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:
	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$
